---
title: "Introduction to MOObject's multiOmicDataSet"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{intro}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


MOObject responsibilities:
- Define and export the S7 class `multiOmicDataSet`.
- Implement object-focused helpers only: constructors, validators, readers, and writers.
- Keep dependencies minimal (prefer base + S7 + lightweight IO packages only).

MOSuite responsibilities:
- Define functions for analysis, modeling, plotting, normalization, filtering, and reporting.
- Import and operate on `multiOmicDataSet` from MOObject.

## Create a multiOmicDataSet

```{r load}
library(MOObject)
moo <- create_multiOmicDataSet_from_files(
  sample_meta_filepath = 'https://raw.githubusercontent.com/CCBR/MOSuite/refs/tags/v0.4.2/inst/extdata/nidap/Sample_Metadata_Bulk_RNA-seq_Training_Dataset_CCBR.csv.gz',
  feature_counts_filepath = 'https://raw.githubusercontent.com/CCBR/MOSuite/refs/tags/v0.4.2/inst/extdata/nidap/Raw_Counts.csv.gz'
)
```

## The multiOmicDataSet object structure

```{r str_moo}
str(moo)
```
